A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-08 paper/paper.tex
wording

  \item The correctness of this encoding depends very strongly on its
    \emph{use}: this only truly encodes contexts if in every case a LF-variable
    is used for $X$.  Moreover, the various well-formedness constraints are a
    bit inelegant, as is the concept of mapping LF variables to indices.

@@

\section{Encoding Telescopes in Higher-Order Abstract Syntax}
More precisely, it seems that what we really need is an encoding of
\emph{telescopes}, in the sense of De Bruijn. A telescope is essentially a
sequence of type assignments, where variables bound earlier may appear free
later, for instance:
\[
  \cdot,x_1:A_1, x_2:A_2(x_1), x_3:A_3(x_1,x_2), \dots, x_n:A_n(x_1,\dots,x_{n-1})
\]

To encode this in a straightforward, higher-order manner, we shall first
stipulate that each variable in the telescope will be an LF-variable. Then,
each type $A_i$ in the telescope will be a term with $i-n$ bindings (i.e.\ it
will be an $i$-ary $\lambda$-abstraction). We'll define by mutual induction a
sort for telescopes $\sorttele$, and a sort for open terms with respect to a
telescope $\sortoexp{\Psi}$:

@@

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``functional sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the functional sequent judgement, we will need the concept of an ``open
categorical judgement''; this is a judgement which has variables from a
telescope free in it.

\subsection{Codes for Open Judgements}
We will define \emph{codes} for such judgements and then
interpret them into proper object judgement (LF-types) later.

@@

The next thing to do is to specify how each of these judgement(-codes) behaves
operationally (i.e. by substituting its outermost variable); we will do so by
extending the LF signature with a new judgement
$\sploot{\mathcal{J}}{\mathcal{J}'}$ (``$\InputMode{\mathcal{J}}$ sploots into
$\OutputMode{\mathcal{J}'}$'') and making it evident on all inputs:

>>>>

  \item The correctness of this encoding depends very strongly on its
    \emph{use}: this only truly encodes contexts if in every case an LF-variable
    is used for $X$.  Moreover, the various well-formedness constraints are a
    bit inelegant, as is the concept of mapping LF variables to De Bruijn indices.

@@

\section{Encoding Telescopes in Higher-Order Abstract Syntax}
More precisely, it seems that what we really need is an encoding of
\emph{telescopes}, in the sense of De Bruijn. A telescope is a
sequence of type assignments, where variables bound earlier may appear free
later; for instance:
\[
  \cdot,x_1:A_1, x_2:A_2(x_1), x_3:A_3(x_1,x_2), \dots, x_n:A_n(x_1,\dots,x_{n-1})
\]

To encode this in a straightforward, higher-order manner, we shall first
stipulate that each variable in the telescope will be an LF-variable. Then,
each type $A_i$ in the telescope will be a term with $i-n$ LF-bindings (i.e.\ it
will be an $i$-ary $\lambda$-abstraction). We'll define by mutual induction a
sort for telescopes $\sorttele$, and a sort for open terms with respect to a
telescope $\sortoexp{\Psi}$:

@@

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``functional sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the functional sequent judgement, we will need the concept of an
``general categorical judgement''; this is a judgement which has variables from
a telescope free in it.

\subsection{Codes for General Judgements}
We will define \emph{codes} for such judgements and then
interpret them into proper object judgements (LF-types) later.

@@

The next thing to do is to specify how each of these judgement(-codes) behaves
operationally (i.e. by substituting its outermost variable); we will do so by
extending the LF signature with a new algorithmic judgement
$\sploot{\mathcal{J}}{\mathcal{J}'}$ (``$\InputMode{\mathcal{J}}$ sploots into
$\OutputMode{\mathcal{J}'}$'') and making it evident on all inputs:
